Privacy and Security Benefits of Jailbreaking iOS

### 2013-12-11 final_project/paper.tex
CPDistributedMessagingCenter sadness…

One such vulnerability\footnote{http://cve.mitre.org/cgi-bin/cvename.cgi?name=CVE-2011-0226} in the PDF rendering engine of Apple iOS\cite{pios}, was successfully used to jailbreak earlier version of iOS by allowing the code necessary to obtain elevated privileges run on the device.

@@

%\subsection{}

>>>>

One such vulnerability\footnote{http://cve.mitre.org/cgi-bin/cvename.cgi?name=CVE-2011-0226} in the PDF rendering engine of Apple iOS\cite{pios}, was successfully used to jailbreak an earlier version of iOS by allowing the code necessary to obtain elevated privileges run on the device.

@@

%\subsection{}
\pagebreak
